\secsweeng{utbildning}{education}

\begin{entrylist}
%------------------------------------------------
\courseentry
    {2020 }
    {{\normalfont Data Engineering with Google Cloud} Specialization}
    {Coursera}
    {\href{https://coursera.org/share/5575917cb72186d2ac385e6a5a04c04e}
        {\sweeng
        {Onlineutbildning med fokus på Google Cloud}
        {Online course track focused on Google Cloud} 
    \footnotesize \faExternalLink}}
    {\sweeng
        {Kurser i data warehousing, skapande och optimering av pipelines, analytics och AI i GCP. }
        {Courses in data warehousing, pipeline creation, analytics and AI, all using Google Cloud products. Currently ongoing.}
    }%
%
\programmeentry
    {2018 - 2020 }
    {\sweeng{Masterexamen {\normalfont i statistik}}{Master of Science {\normalfont in Statistics}}}
    {\sweeng{Linköpings Universitet}{Linköping University}}
    {\href{https://liu.se/en/education/program/f7msl}
        {\sweeng
        {Internationellt Masterprogram i statistik och maskininlärning}
        {International Master´s Programme in Statistics and Machine Learning} 
    \footnotesize \faExternalLink}}
    {\href
        {http://urn.kb.se/resolve?urn=urn\%3Anbn\%3Ase\%3Aliu\%3Adiva-170759}
        {Automatic map generation from nation-wide data sources using deep learning \footnotesize \faExternalLink} 
    }
    {\sweeng
        {Valbara kurser inom bl.a. tidsserianalys, avancerad maskininlärning och visualiseringstekniker.}
        {Elective courses on time series analysis, advanced machine learning and visualisation techniques.}
    }{}%
%
\programmeentry
    {2015 - 2018 }
    {\sweeng{Kandidatexamen {\normalfont i statistik}}{Bachelor of Science {\normalfont in Statistics}}}
    {\sweeng{Linköpings Universitet}{Linköping University}}
    {\href{https://liu.se/utbildning/program/f7ksa}
        {\sweeng
        {Kandidatprogram i statistik och dataanalys}
        {Bachelor´s Programme in Statistics and Data Analysis} 
    \footnotesize \faExternalLink}}
    {\sweeng
        {Sekvensanalys av hur småkunders omsättningsmönster påverkades när de uppvaktades av säljorganisationen.}
        {Sequential analysis of how the revenue patterns of smaller customers were affected by the sales organisation. }
    }
    {\sweeng
    {Valbara kurser med fokus på matematik. Projektarbete om visaulisering av produktionsutfall vid ett pappersbruk.}
    {Elective courses focused on mathematics. Project work on visualisation of quality in paper mill production.}
    }{}

%------------------------------------------------
\end{entrylist}
